Are populations like a circuit? Comparing isolation by resistance to a new coalescent-based method.

### 2019-04-22 review-responses.tex

\vskip 1em

We are writing to submit a revised version of our manuscript, 
``Are populations like a circuit? 
Comparing isolation by resistance to a new coalescent-based method.''
(formerly titled 
``Are populations like a circuit? 
The relationship between isolation by distance and isolation by resistance'').

Thanks to the five mostly anonymous reviewers for their many useful comments --
we've addressed all of them, which we think has made the paper more generally understandable
and suitable for this audience.
In particular, we have included analysis of an empirical dataset 
(which was fun, and produced good results),
revised the figures for increased legibility,
and added a substantial amount of additional explanation of the technical points.
We hope that discussion of the empirical results should help make interpretation
of the coalescent-based model more broadly understandable.
And, at the suggestion of reviewer 1,
we have changed the title.
We think this has all improved the paper substantially,
and hope you agree.

We have included detailed responses to all the reviewer's comments,
with page and line numbers that refer to the revised version of the manuscript.
We are also including a file with changes made since the first submission highlighted
(named \texttt{ibc-diff.pdf}).
Finally, we are including an additional pdf (named \texttt{isolation\_by\_coalescence.pdf})
that has the paper, the supplementary material, and the responses to reviewers all in one place
in which the page/line numbers in the reviews are hyperlinks 
to the correct location in the main document.

### 2019-04-22 isolation_by_coalescence.tex
actual submission

We also applied our method to genotyping data from 423 samples of \textit{Populus trichocarpa}
and 8 samples of the closely related \textit{Populus balsamifera} (with which it hybridizes),
from a large region of northwestern North America,
described in \citet{geraldes2014landscape}.
These data \citep{geraldes2014data},
include geographical coordinates and genotypes from a genotyping chip targeting 34K SNPs.
In addition to preliminary filtering described in \citet{geraldes2014landscape},
we additionally removed 2,314 SNPs with more than 5\% missing data, retaining 30,756 SNPs,
and two individuals, one with more than 15\% missing data and one that is much further east
than all the other samples.
We then computed pairwise divergence between the remaining samples.
We discretized the landscape manually into nine regions,
preserving species boundaries and choosing divisions along gaps in sampling
to keep geographic areas roughly equal.
The numbers of samples included in each discretized region varied from 1 to 268,
but our method does not assume equal sample numbers
(however, an $F_{ST}$-based method would likely be affected by such large differences in sampling).

%%%%%%%%%%%%%%%%
\subsection*{Code availability}

All code used for this work is available at \url{https://github.com/elundgre/gene-flow-inference}
(including an R package that implements the MCMC method)
and \url{https://github.com/petrelharp/isolation_by_coalescence} (including the SLiM simulations).

>>>>

We also applied our method to genotyping data from 423 samples of \textit{Populus trichocarpa}
and 8 samples of the closely related \textit{Populus balsamifera} (with which it hybridizes),
from a large region of northwestern North America,
described in \citet{geraldes2014landscape}.
These data 
include geographical coordinates and genotypes from a genotyping chip targeting 34K SNPs.
In addition to preliminary filtering described in \citet{geraldes2014landscape},
we additionally removed 2,314 SNPs with more than 5\% missing data, retaining 30,756 SNPs,
and two individuals, one with more than 15\% missing data and one that is much further east
than all the other samples.
We then computed pairwise divergence between the remaining samples.
We discretized the landscape manually into nine regions,
preserving species boundaries and choosing divisions along gaps in sampling
to keep geographic areas roughly equal.
The numbers of samples included in each discretized region varied from 1 to 268,
but our method does not assume equal sample numbers
(however, an $F_{ST}$-based method would likely be affected by such large differences in sampling).

%%%%%%%%%%%%%%%%
\subsection*{Code and data availability}

All code used for this work is available at \url{https://github.com/elundgre/gene-flow-inference}
(including an R package that implements the MCMC method)
and \url{https://github.com/petrelharp/isolation_by_coalescence} (including the SLiM simulations).
Sequencing data for \textit{Populus} is available from Data Dryad \citep{geraldes2014data}.
